---
title: "EDA: Ramen Rater"
output: html_notebook
---


```{r setup}
library(tidyverse)
```

This code loads and cleans the ramen data set.

```{r load}
ramen <- read_csv("ramen-ratings.csv",
                col_types = "iccccdc",
                na = c("Unrated", "\n")) %>%
  rename(id = `Review #`, top_ten = `Top Ten`) %>%
  mutate(top_ten_year = str_sub(top_ten, end=4) %>%
           as.integer(),
         top_ten = str_sub(top_ten, 7) %>%
           as.integer()) %>%
  mutate_at(vars(Brand, Variety, Style, Country),tolower)
names(ramen) <- tolower(names(ramen))
```

Ramen is now a tibble with reasonably easy to use columns all letters are now lower case and numbers are correctly coded as doubles or integers

The data set below splits up the variety column so each word in the variety is in its own row this will make it easier to detect words.

```{r long}
ramen_long <- ramen %>%
  mutate(variety = str_split(variety, " ")) %>%
  unnest(variety)
```

For example here are all the varieties with chicken

```{r chicken}
ramen_long %>% group_by(variety) %>%
  filter(variety == "chicken")
```
